\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing income inequality with tax data - Switzerland from 1917 to 2010}

### 2015-06-16 paper/subdocuments/results.Rnw
tiny changes in the results part...

#bern kantonal (liegt lokal wegen datenschutz)
try(bern_kt<-read.dta("U:/Persönlich/Forschung/Uni Bern/taxdata_BE_12.dta"))
try(bern_kt <- read.csv("G:/stick/bern//BFH-Grunddaten 2012 Output V1.1.csv",sep=";"))
#> nrow(bern_kt)
#[1] 622368
nrow(filter(bern_kt,VON=="2012-01-01",BIS=="2012-12-31"))
#[1] 605975 wir filtern ca. 3% unterjährige
bern_kt <- filter(bern_kt,VON=="2012-01-01",BIS=="2012-12-31")
bern_kt <- filter(bern_kt,Satzeink_BUND<=TOTEINK,erm==0)
bern_kt <- filter(bern_kt,erm==0)
names(bern_kt)<-tolower(names(bern_kt))
set0 <- function(x) ifelse(x<0 | is.na(x),0,x)
bern_kt <- bern_kt %>% mutate(primeink2 = set0(hem)+set0(nem)+set0(esm)+set0(sgm)+set0(hef)+set0(nef)+set0(esf)+set0(sgf)+set0(erfolg_s)+set0(erfolg_l)+set0(kk_ertrag)+set0(bg_ertrag)+ set0(wsert)+set0(eink_lieg)+set0(eg_ertrag)+set0(stm)+set0(stf)+set0(lov)+set0(lmv)+set0(lng))

@@

<<bern_kantonale_analysen>>=
# core variables from bern 2002-2012
try(bern <- read.dta("G:/stick/bern/mini_taxdata_BE_all.dta"))
try(bern<-read.dta("P:/WGS/FBS/ISS/Projekte laufend/SNF Ungleichheit/Datengrundlagen/Kantonale Steuerdaten/Bern/taxdata_BE_reduced.dta"))
P:\WGS\FBS\ISS\Projekte laufend\SNF Ungleichheit\Datengrundlagen\Kantonale Steuerdaten\Bern
bern <- filter(bern_kt,Satzeink_BUND<=TOTEINK,erm==0)
bern <- filter(bern_kt,erm==0)
bern$verfeink<-bern$TOTEINK+bern$privattrans_bez-bern$steuertotal

@@

# wide to long
bern_gini_long <- melt(bern_gini,id.vars="stj",variable.name="Income",value.name="Gini")

# legend order
levels(bern_gini_long$Income) <- c("total income", "taxable income", "Disposable income")
bern_gini_long$Income <- factor(bern_gini_long$Income,levels=c("total income", "taxable income", "Disposable income")

fig_bern_gini <- ggplot(bern_gini_long, aes(x=stj,y=Gini)) +
  #scale_y_continuous(limits=c(0.28,0.55))+
  scale_x_continuous(breaks=number_ticks(5)) +
  geom_point(aes(shape=Income),size=pointsize)+
  geom_line(aes(linetype=Income),size=linesize)+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))+
  ggtitle("Gini coefficients of different income concepts")
fig_bern_gini

>>>>

#bern kantonal (liegt lokal wegen datenschutz)
try(bern_kt<-read.dta("U:/Persönlich/Forschung/Uni Bern/taxdata_BE_12.dta"))
try(bern_kt <- read.csv("G:/stick/bern//BFH-Grunddaten 2012 Output V1.1.csv",sep=";"))
#> nrow(bern_kt)
#[1] 622368
nrow(filter(bern_kt,VON=="2012-01-01",BIS=="2012-12-31"))
#[1] 605975 wir filtern ca. 3% unterjährige
bern_kt <- filter(bern_kt,VON=="2012-01-01",BIS=="2012-12-31")
bern_kt <- filter(bern_kt,Satzeink_BUND<=TOTEINK)
bern_kt <- filter(bern_kt,erm==0)
names(bern_kt)<-tolower(names(bern_kt))
set0 <- function(x) ifelse(x<0 | is.na(x),0,x)
bern_kt <- bern_kt %>% mutate(primeink2 = set0(hem)+set0(nem)+set0(esm)+set0(sgm)+set0(hef)+set0(nef)+set0(esf)+set0(sgf)+set0(erfolg_s)+set0(erfolg_l)+set0(kk_ertrag)+set0(bg_ertrag)+ set0(wsert)+set0(eink_lieg)+set0(eg_ertrag)+set0(stm)+set0(stf)+set0(lov)+set0(lmv)+set0(lng))

@@

<<bern_kantonale_analysen>>=
# core variables from bern 2002-2012
try(bern <- read.dta("G:/stick/bern/mini_taxdata_BE_all.dta"))
try(bern<-read.dta("P:/WGS/FBS/ISS/Projekte laufend/SNF Ungleichheit/Datengrundlagen/Kantonale Steuerdaten/Bern/taxdata_BE_reduced.dta"))

bern$verfeink<-bern$TOTEINK+bern$privattrans_bez-bern$steuertotal

@@

# wide to long
bern_gini_long <- melt(bern_gini,id.vars="stj",variable.name="Income",value.name="Gini")
names(bern_gini_long)<-c("stj","Income","Gini")
# legend order
levels(bern_gini_long$Income) <- c("total income", "taxable income", "Disposable income")
bern_gini_long$Income <- factor(bern_gini_long$Income,levels=c("total income", "taxable income", "Disposable income"))

fig_bern_gini <- ggplot(bern_gini_long, aes(x=stj,y=Gini)) +
  scale_y_continuous(limits=c(0.28,0.55))+
  scale_x_continuous(breaks=number_ticks(5)) +
  geom_point(aes(shape=Income),size=5)+
  geom_line(aes(linetype=Income),size=1)+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 0.3))+
  ggtitle("Gini coefficients of different income concepts")
fig_bern_gini
